Meshpoint optimization

### 2022-04-22 notes/index.Rmd
link to github *pages*

[Exploring different ways of fitting random effects GAMs](notes/environmental-stochasticity.html)

[Why is stochastic lambda \> deterministic?](notes/understanding-stochastic-lambda.html)

[Optimizing the number of meshpoints](notes/optimizing-meshpoints.html)

>>>>

[Exploring different ways of fitting random effects GAMs](https://brunalab.github.io/lagged-ipms/notes/environmental-stochasticity.html)

[Why is stochastic lambda \> deterministic?](https://brunalab.github.io/lagged-ipms/notes/understanding-stochastic-lambda.html)

[Optimizing the number of meshpoints](https://brunalab.github.io/lagged-ipms/notes/optimizing-meshpoints.html)
